---
title: "Exponential models with Quantix imagery"
author: "S. Sunoj"
date: "3/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r, message=FALSE}
# rm(list = ls())
 library(tictoc)  # to monitor time

library(raster) # read raster files
library(rgdal) # Use GDAL functions
library(exactextractr) # Zonal statistics from raster
library(sf) # Working with shapefile layers

library(tidyverse) # data wrangling
library(plyr) # data wrangling
library(dplyr) # data wrangling

library(ggpmisc) # To place geom_text within plot
# library(ggmap) # Plot leaflet
# library(ggplot2) # Visualizations
library(plotly) # Interactive visualization

print("Packages loaded successfully!")

```

# Functions specific to this RMD
```{r, echo=FALSE}
#########################################
# Creating function for exponential fit
myexpfit <- function(response_var, pred_var, mydata){
  # print(paste0("Model = ", "log(",response_var, ")~", pred_var))
  model.linear <- lm(paste0("log(",response_var, ")~", pred_var), data = mydata)
   a1 <- exp(model.linear$coefficients[1])
   b1 <- (model.linear$coefficients[2])
   R2 <- summary(model.linear)$r.squared

   myresults <- c(a1, b1, R2)
   return(myresults)
}
#########################################

# My GGPLOT for yield map
my_yield_plot <- function(yield_df){
  fieldtitle <- levels(yield_df$Fieldname)
  # Legend labeling - Splitting the yield range into equal classes
  minyld <- round(min(yield_df$Yield_Mg.ha),0) # minimum yield 
  maxyld <- round(max(yield_df$Yield_Mg.ha),0) # maximum yield
  Nclasses <- 4      # Number of yield classes to split from the whole yield range
  
  mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
  YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")

  yld_plot <- ggplot(yield_df, aes(x = Longitude, y = Latitude)) +
  geom_point(aes(color = Yield_Mg.ha), size = 0.7) +    
      theme_bw() +
      # facet_grid(Field~Year, scales = "free") +
      theme(aspect.ratio = 1.0) +
      ggtitle("Actual yield (Mg/ha)")+
      facet_wrap(~Fieldname, scales = "free") +
      # theme(legend.position = c(0.85, 0.27))+
      scale_colour_gradientn(colours = YE_colors,  
                             name = "Yield (Mg/ha)", 
                             limits=c(minyld,maxyld),
                             breaks = mybreaks,
                             labels = round(mybreaks, 0)) +
    guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
    theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks = element_blank(), 
            plot.title = element_text(size=14, face = "bold")) +
      theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
            legend.text = element_text(vjust = 0.5),
            strip.text = element_text(face = "bold", size = 10))
  yld_plot
  
}

#########################################
my_pred_plot <- function(sub_dat){
  fieldtitle <- levels(sub_dat$Fieldname)
    # Legend labeling - Splitting the yield range into equal classes
  minyld <- round(min(sub_dat$Pred_Yield),0) # minimum yield 
  maxyld <- round(max(sub_dat$Pred_Yield),0) # maximum yield
  Nclasses <- 4      # Number of yield classes to split from the whole yield range
    
  mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
  YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")

  pred_map <- ggplot(sub_dat, aes(x = Longitude, y = Latitude)) +
        geom_point(aes(color = Pred_Yield), size = 0.7) +    
        theme_bw() +
        # facet_grid(Field~Year, scales = "free") +
        theme(aspect.ratio = 1.0) +
        ggtitle("Predicted yield (Mg/ha)")+
        facet_wrap(~Fieldname, scales = "free") +
        # theme(legend.position = c(0.85, 0.27))+
        scale_colour_gradientn(colours = YE_colors,  
                               name = "Yield (Mg/ha)", 
                               limits=c(minyld,maxyld),
                               breaks = mybreaks,
                               labels = round(mybreaks, 0)) +
        guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(), 
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks = element_blank(), 
              plot.title = element_text(size=14, face = "bold")) +
        theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
              legend.text = element_text(vjust = 0.5),
              strip.text = element_text(face = "bold", size = 10))
  pred_map
}
#==============



```

# Load dataset
```{r, message=FALSE, warning=FALSE}

# dat <- read.csv("deep-learning-all-features.csv", header = TRUE)
# save(dat, file = "Quantix_deep_learning.RData")

load("Quantix_deep_learning.RData", verbose = TRUE)

str(dat)
# colnames(dat)[5] <- "Latitude"
# colnames(dat)[6] <- "Longitude"

# save(dat, file = "Quantix_deep_learning.RData")

```
# Data preprocessing
## Check for missing values
```{r}
# Check if any columns have missing values 
sapply(dat, anyNA)

# Names of columns that has missing values
names(dat)[sapply(dat, anyNA)]

```

# Plot individual field yield data
```{r}

# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
selfield <- "DMD_GH1"

sub_dat <- dat %>%
  dplyr::filter(Fieldname == selfield) %>%
  droplevels()

# Legend labeling - Splitting the yield range into equal classes
minyld <- round(min(sub_dat$Yield_Mg.ha),0) # minimum yield 
maxyld <- round(max(sub_dat$Yield_Mg.ha),0) # maximum yield
Nclasses <- 4      # Number of yield classes to split from the whole yield range

mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")

my_yield_plot(sub_dat)

# png_save_name <- paste(selfield, "_", "allYear", ".png", sep = "")
# 
# wd <- 8.5
# ht <- 3 
# ggsave(png_save_name, width = wd, height = ht, unit = "in")

```

# Plot all yield data
```{r}
g_dat <- dat %>%
  dplyr::filter(Type == "grain") %>%
  droplevels()

my_yield_plot(g_dat)

s_dat <- dat %>%
  dplyr::filter(Type == "silage") %>%
  droplevels()

my_yield_plot(s_dat)

```

# Exploratory data analysis
## Distribution plots
```{r}
# Violin plot

vplt <- ggplot(dat, aes(x = Fieldname, y = Yield_Mg.ha, fill = Fieldname)) +
  geom_violin() +
  theme_bw() +
  facet_wrap(~Type, nrow = 2, scales = "free_y")

vplt


dplt <- ggplot(dat, aes(x = Yield_Mg.ha, y = ..scaled.., fill = Fieldname)) +
  # geom_violin() +
  geom_density(alpha = 0.4, size = 1) + 
  theme_bw() +
  facet_wrap(~Type, nrow = 2, scales = "free")

dplt


```

## GPS points vs yield
```{r}

# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
# selfield <- "DMD_GH1"

sub_datf <- dat %>% 
  filter(Week == 1 & Type == "grain") %>% 
  droplevels()

# Legend labeling - Splitting the yield range into equal classes
minyld <- round(min(sub_datf$Yield_Mg.ha),0) # minimum yield 
maxyld <- round(max(sub_datf$Yield_Mg.ha),0) # maximum yield
Nclasses <- 4      # Number of yield classes to split from the whole yield range

mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")

#=====================
lat_plot <- ggplot(sub_datf, aes(x = Latitude, y = Yield_Mg.ha)) +
  geom_point(aes(color = Yield_Mg.ha), size = 0.7) +    
      theme_bw() +
      # facet_grid(Field~Year, scales = "free") +
      theme(aspect.ratio = 1.0) +
      ggtitle("Latitude vs Yield")+
      facet_wrap(~Fieldname, scales = "free") +
      # theme(legend.position = c(0.85, 0.27))+
      scale_colour_gradientn(colours = YE_colors,  
                             name = "Yield (Mg/ha)", 
                             limits=c(minyld,maxyld),
                             breaks = mybreaks,
                             labels = round(mybreaks, 0)) +
    guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
    theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            # axis.title.x = element_blank(), 
            # axis.title.y = element_blank(),
            # axis.text.x = element_blank(), 
            # axis.text.y = element_blank(), 
            axis.ticks = element_blank(), 
            plot.title = element_text(size=14, face = "bold")) +
      theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
            legend.text = element_text(vjust = 0.5),
            strip.text = element_text(face = "bold", size = 10))
lat_plot

#=====================
long_plot <- ggplot(sub_datf, aes(x = Longitude, y = Yield_Mg.ha)) +
  geom_point(aes(color = Yield_Mg.ha), size = 0.7) +    
      theme_bw() +
      # facet_grid(Field~Year, scales = "free") +
      theme(aspect.ratio = 1.0) +
      ggtitle("Longitude vs Yield")+
      facet_wrap(~Fieldname, scales = "free") +
      # theme(legend.position = c(0.85, 0.27))+
      scale_colour_gradientn(colours = YE_colors,  
                             name = "Yield (Mg/ha)", 
                             limits=c(minyld,maxyld),
                             breaks = mybreaks,
                             labels = round(mybreaks, 0)) +
    guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
    theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            # axis.title.x = element_blank(), 
            # axis.title.y = element_blank(),
            # axis.text.x = element_blank(), 
            # axis.text.y = element_blank(), 
            axis.ticks = element_blank(), 
            plot.title = element_text(size=14, face = "bold")) +
      theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
            legend.text = element_text(vjust = 0.5),
            strip.text = element_text(face = "bold", size = 10))
long_plot


```
#-----------------------------
# Approach 1
## 1.a. Use only strip data for exponential model
```{r}

# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
# "1"  "2"  "3"  "4"  "5"  "6"  "7"  "8"  "9"  "10" "11" "12" "13" "14"
# Best grain field - DMD_GH1
# Best sialge filed - SSF_121, PSF_12

selfield <- "DMD_GH1"
# seltype <- "silage"

sub_dat <- dat %>% 
  filter(!is.na(N) & Fieldname == selfield) %>% 
  droplevels()

my_yield_plot(sub_dat)

# "1"  "2"  "3"  "4"  "5"  "6"  "7"  "8"  "9"  "10" "11" "12" "13" "14"
lvl <- levels(sub_dat$Week)
sub_dat$Strip <- as.numeric(sub_dat$Strip)

# NDVI, GNDVI, EXG, EVI2, EVI, SR, TGI, 
#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(sub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- sub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()
  
  mod <- myexpfit("Yield_Mg.ha", "NDVI", wsub_dat)
  
  ## RMSE calculation ======
  a_fit <- as.numeric(mod[1])
  b_fit <- as.numeric(mod[2])
  rsq <- as.numeric(mod[3])
  
  ssub_dat <- dat %>% 
    filter(Week == lvl[i] & Fieldname == selfield) %>% 
    droplevels() 
    
  ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat$NDVI)

  ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
  sqe <- (ssub_dat$error^2)
  mse <- mean(sqe)
  rmse_week <- sqrt(mse)
  cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
  # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
  ## ========================
  
  r2 <- as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week))
  r2df <- rbind(r2df, r2)
  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE")
str(r2df)

#============================
## Pick the best week
# best_week <- which.max(r2df$R2)
best_week <- which.min(r2df$RMSE)
  
sub_dat1 <- dat %>% 
  filter(Week == best_week & Fieldname == selfield) %>% 
  droplevels()

a_coeff <- r2df[best_week, 2]
b_coeff <- r2df[best_week, 3]

cat("a_best = ", a_coeff, "; b_best = ", b_coeff)

sub_dat1$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat1$NDVI)

my_pred_plot(sub_dat1)
my_yield_plot(sub_dat1)

sub_dat1$error <- (sub_dat1$Pred_Yield - sub_dat1$Yield_Mg.ha)
mse <- mean(sub_dat1$error^2)
rmse <- sqrt(mse)
cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")

#======================
# Secondary axis plot
d  <- r2df
x  <- 'Weeks'
y1 <- 'R2'
y2 <- 'RMSE'

a            <- range(d[[y1]])
b            <- range(d[[y2]])
scale_factor <- diff(a)/diff(b)
d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]

trans <- ~ ((. - a[1]) / scale_factor) + b[1]

r2_rmse_plt <- ggplot(d) +
              geom_point(aes_string(x, y1)) + 
              geom_line(aes_string(x, y1)) + 
              geom_point(aes_string(x, y2), col='red') + 
              geom_line(aes_string(x, y2), col='red') +
              ggtitle(selfield) + 
              theme_bw()+
              theme(legend.position = c(0.8, 0.7)) + 
              scale_x_continuous(breaks = seq(1,15, 1))+
              scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))

r2_rmse_plt

ggplotly(r2_rmse_plt)
```

## 1.b. Use 10 and 90 percentile of strip data
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
selfield <- "DMD_GH1"

sub_dat <- dat %>% 
  filter(!is.na(N) & Fieldname == selfield) %>% 
  droplevels()

my_yield_plot(sub_dat)

# Evaluate qunatile cutoffs
pert <- 0.10

cutoffs <- quantile(sub_dat$Yield_Mg.ha, c(pert, (1-pert)))
cat("Cutoff for field", selfield, " =", cutoffs)

# Subset points within cutoff
qsub_dat <- sub_dat %>% 
  filter(Yield_Mg.ha <= cutoffs[[1]] | Yield_Mg.ha >= cutoffs[[2]]) %>% 
  droplevels()

my_yield_plot(qsub_dat)

#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(qsub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

lvl <- levels(qsub_dat$Week)

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- qsub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()
  
  mod <- myexpfit("Yield_Mg.ha", "NDVI", wsub_dat)
  
  ## RMSE calculation ======
  a_fit <- as.numeric(mod[1])
  b_fit <- as.numeric(mod[2])
  rsq <- as.numeric(mod[3])
  
  ssub_dat <- dat %>% 
    filter(Week == lvl[i] & Fieldname == selfield) %>% 
    droplevels() 
    
  ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat$NDVI)

  ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
  sqe <- (ssub_dat$error^2)
  mse <- mean(sqe)
  rmse_week <- sqrt(mse)
  cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
  # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
  ## ========================
  
  r2 <- as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week))
  r2df <- rbind(r2df, r2)
  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE")
str(r2df)


num_cols <- c("Weeks", "a", "b", "R2")
r2df[num_cols] <- lapply(r2df[num_cols], as.numeric)

r2plot <- ggplot(r2df, aes(x = Weeks, y = R2)) +
  geom_point(size = 2) +
  geom_line() +
  theme_bw() + 
  ggtitle(paste0(pert*100, "% and ", (1-pert)*100, "% data from N strips")) + 
  scale_y_continuous(breaks = seq(0,1.0, 0.1)) +
  scale_x_continuous(breaks = seq(1,15, 1))

# r2plot
ggplotly(r2plot)

#==========================================
## Select best week and evaluate RMSE
best_week <- which.max(r2df$R2)

sub_dat2 <- dat %>% 
  filter(Week == best_week & Fieldname == selfield)

a_coeff <- r2df[best_week, 2]
b_coeff <- r2df[best_week, 3]

sub_dat2$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat2$NDVI)
my_yield_plot(sub_dat2)
my_pred_plot(sub_dat2)

sub_dat2$error <- (sub_dat2$Pred_Yield - sub_dat2$Yield_Mg.ha)
se <- (sub_dat2$error^2)
mse <- mean(se)
rmse <- sqrt(mse)
cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")

#======================
# Secondary axis plot
d  <- r2df
x  <- 'Weeks'
y1 <- 'R2'
y2 <- 'RMSE'

a            <- range(d[[y1]])
b            <- range(d[[y2]])
scale_factor <- diff(a)/diff(b)
d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]

trans <- ~ ((. - a[1]) / scale_factor) + b[1]

r2_rmse_plt <- ggplot(d) +
              geom_point(aes_string(x, y1)) + 
              geom_line(aes_string(x, y1)) + 
              geom_point(aes_string(x, y2), col='red') + 
              geom_line(aes_string(x, y2), col='red') +
              ggtitle(selfield) + 
              theme_bw()+
              theme(legend.position = c(0.8, 0.7)) + 
              scale_x_continuous(breaks = seq(1,15, 1))+
              scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))

# r2_rmse_plt
ggplotly(r2_rmse_plt)

```

# Approach 2
## 2.a. Use whole data without strip (select N == NA)
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
selfield <- "DMD_GH1"

sub_dat <- dat %>% 
  filter(is.na(N) & Fieldname == selfield) %>% 
  droplevels()

my_yield_plot(sub_dat)

#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(sub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

lvl <- levels(sub_dat$Week)

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- sub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()
  
  mod <- myexpfit("Yield_Mg.ha", "NDVI", wsub_dat)
  
  ## RMSE calculation ======
  a_fit <- as.numeric(mod[1])
  b_fit <- as.numeric(mod[2])
  rsq <- as.numeric(mod[3])
  
  ssub_dat <- dat %>% 
    filter(Week == lvl[i] & Fieldname == selfield) %>% 
    droplevels() 
    
  ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat$NDVI)

  ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
  sqe <- (ssub_dat$error^2)
  mse <- mean(sqe)
  rmse_week <- sqrt(mse)
  cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
  # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
  ## ========================
  
  r2 <- as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week))
  r2df <- rbind(r2df, r2)
  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE")
str(r2df)

#==========================================
## Select best week and evaluate RMSE
best_week <- which.max(r2df$R2)

sub_dat3 <- dat %>% 
  filter(Week == best_week & Fieldname == selfield)

a_coeff <- r2df[best_week, 2]
b_coeff <- r2df[best_week, 3]

sub_dat3$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat3$NDVI)

sub_dat3$error <- (sub_dat3$Pred_Yield - sub_dat3$Yield_Mg.ha)
mse <- mean(sub_dat3$error^2)
rmse <- sqrt(mse)
cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")

#======================
# Secondary axis plot
d  <- r2df
x  <- 'Weeks'
y1 <- 'R2'
y2 <- 'RMSE'

#-----------------------------------------------------------------------------
# Rescale the second y axis by 
#   - subtracting its minimum value (to set it to start at 0)
#   - scaling so that it has the same range as the 'y1' variable
#   - offsettting it by the minimum value of y1
#-----------------------------------------------------------------------------
a            <- range(d[[y1]])
b            <- range(d[[y2]])
scale_factor <- diff(a)/diff(b)
d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]

#-----------------------------------------------------------------------------
# Need to define the second axis transformation to be the inverse of the data
# transformation to everything cancels out appropriately
#-----------------------------------------------------------------------------
trans <- ~ ((. - a[1]) / scale_factor) + b[1]

#-----------------------------------------------------------------------------
# tell the y axis to set up a scaled secondary axis with the given transform
#-----------------------------------------------------------------------------
r2_rmse_plt <- ggplot(d) +
              geom_point(aes_string(x, y1)) + 
              geom_line(aes_string(x, y1)) + 
              geom_point(aes_string(x, y2), col='red') + 
              geom_line(aes_string(x, y2), col='red') +
              ggtitle(selfield) + 
              theme_bw()+
              theme(legend.position = c(0.8, 0.7)) + 
              scale_x_continuous(breaks = seq(1,15, 1))+
              scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))

r2_rmse_plt

ggplotly(r2_rmse_plt)

```

## 2.b. Use 10 and 90 percentile of strip data
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
selfield <- "DMD_GH1"

sub_dat <- dat %>% 
  filter(is.na(N) & Fieldname == selfield) %>% 
  droplevels()

my_yield_plot(sub_dat)

# Evaluate qunatile cutoffs
pert <- 0.10
cutoffs <- quantile(sub_dat$Yield_Mg.ha, c(pert, (1-pert)))
cat("Cutoff for field", selfield, " =", cutoffs)

# Subset points within cutoff
qsub_dat <- sub_dat %>% 
  filter(Yield_Mg.ha <= cutoffs[[1]] | Yield_Mg.ha >= cutoffs[[2]]) %>% 
  droplevels()

my_yield_plot(qsub_dat)

#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(qsub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

lvl <- levels(qsub_dat$Week)

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- sub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()
  
  mod <- myexpfit("Yield_Mg.ha", "NDVI", wsub_dat)
  
  ## RMSE calculation ======
  a_fit <- as.numeric(mod[1])
  b_fit <- as.numeric(mod[2])
  rsq <- as.numeric(mod[3])
  
  ssub_dat <- dat %>% 
    filter(Week == lvl[i] & Fieldname == selfield) %>% 
    droplevels() 
    
  ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat$NDVI)

  ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
  sqe <- (ssub_dat$error^2)
  mse <- mean(sqe)
  rmse_week <- sqrt(mse)
  cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
  # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
  ## ========================
  
  r2 <- as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week))
  r2df <- rbind(r2df, r2)
  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE")
str(r2df)

# ggplotly(r2plot)

#==========================================
## Select best week and evaluate RMSE
best_week <- which.max(r2df$R2)

sub_dat4 <- dat %>% 
  filter(Week == best_week & Fieldname == selfield)

a_coeff <- r2df[best_week, 2]
b_coeff <- r2df[best_week, 3]

sub_dat4$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat4$NDVI)

sub_dat4$error <- (sub_dat4$Pred_Yield - sub_dat4$Yield_Mg.ha)
mse <- mean(sub_dat4$error^2)
rmse <- sqrt(mse)
cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")

#======================
# Secondary axis plot
d  <- r2df
x  <- 'Weeks'
y1 <- 'R2'
y2 <- 'RMSE'

#-----------------------------------------------------------------------------
# Rescale the second y axis by 
#   - subtracting its minimum value (to set it to start at 0)
#   - scaling so that it has the same range as the 'y1' variable
#   - offsettting it by the minimum value of y1
#-----------------------------------------------------------------------------
a            <- range(d[[y1]])
b            <- range(d[[y2]])
scale_factor <- diff(a)/diff(b)
d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]

#-----------------------------------------------------------------------------
# Need to define the second axis transformation to be the inverse of the data
# transformation to everything cancels out appropriately
#-----------------------------------------------------------------------------
trans <- ~ ((. - a[1]) / scale_factor) + b[1]

#-----------------------------------------------------------------------------
# tell the y axis to set up a scaled secondary axis with the given transform
#-----------------------------------------------------------------------------
r2_rmse_plt <- ggplot(d) +
              geom_point(aes_string(x, y1)) + 
              geom_line(aes_string(x, y1)) + 
              geom_point(aes_string(x, y2), col='red') + 
              geom_line(aes_string(x, y2), col='red') +
              ggtitle(selfield) + 
              theme_bw()+
              theme(legend.position = c(0.8, 0.7)) + 
              scale_x_continuous(breaks = seq(1,15, 1))+
              scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))

r2_rmse_plt

ggplotly(r2_rmse_plt)

```

# Cumulative distribution plot per CropType
```{r}
# Subset grain or silage
crop_dat <- dat %>% 
  filter(Type == "grain") %>% 
  droplevels()

g_cum_dist_plot <- ggplot(crop_dat, aes(Yield_Mg.ha)) +
  stat_ecdf(aes(color = Fieldname), geom = "step") +
  theme_bw()

g_cum_dist_plot

# Silage yield cumulative distribution
crop_dat <- dat %>% 
  filter(Type == "silage") %>% 
  droplevels()

s_cum_dist_plot <- ggplot(crop_dat, aes(Yield_Mg.ha)) +
  stat_ecdf(aes(color = Fieldname), geom = "step") +
  theme_bw()

s_cum_dist_plot

#===========================
hist_plot <- ggplot(crop_dat, aes(x = Yield_Mg.ha, y = ..scaled.., fill = Fieldname)) +
  # stat_ecdf(aes(color = Fieldname), geom = "step") +
  geom_density(aes(color = Fieldname), alpha = 0.2) + 
  theme_bw()

hist_plot

```

#-----------------------------
# Weather vs VI - working
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
# "1"  "2"  "3"  "4"  "5"  "6"  "7"  "8"  "9"  "10" "11" "12" "13" "14"
# Best grain field - DMD_GH1
# Best silage field - SSF_121, PSF_12

selfield <- "DMD_GH1"
# seltype <- "silage"

sub_dat <- dat %>% 
  filter(Fieldname == selfield) %>% 
  droplevels()

dep_var <- c("rgn_red", "rgn_green", "rgn_nir", "rgb_red", "rgb_green", "rgb_blue", "NDVI", "GNDVI", "EVI2", "SR", "EXG", "TGI")

mu <- ddply(sub_dat, "Week", summarise, ndvi.mean = mean(NDVI), weather.mean = mean(ACIS_GDD))
head(mu)

plt1 <- ggplot(mu, aes(x = weather.mean, y = ndvi.mean)) + 
          # geom_boxplot() +
          # ggtitle(dep_var[i]) + 
          geom_point(size = 2.5) + 
          geom_line() + 
          theme_bw() + 
          xlab("Weather") + 
          ylab("NDVI")

plt1


```

#-----------------------------
# Subset only N strip data
```{r}

ndat <- dat %>% 
  filter(!is.na(N)) %>% 
  droplevels()

names(ndat)[sapply(ndat, anyNA)]

```

# NDVI plots across weeks
```{r}

sel_dat <- dat %>% 
  filter(Fieldname == selfield) %>% 
  droplevels()
  
nplt <- ggplot(sel_dat, aes(x = Latitude, y = Longitude)) +
  geom_point(aes(color = NDVI), size = 0.7) + 
  theme_bw() + 
  theme(aspect.ratio = 1.0) +
  facet_wrap(~Week, nrow = 2) 

nplt

```


# NDVI box plots for all weeks
```{r}

# selfield <- "PSF_12"

ndat <- dat %>% 
  filter(!is.na(N) & Fieldname == selfield) %>% 
  droplevels()

ndvi_plot <- ggplot(ndat, aes(x = Week, y = NDVI)) + 
  geom_boxplot() + 
  theme_bw()

ndvi_plot

```




# Save actual and predicted yield into a CSV
```{r}

sel_dat <- sub_dat %>% 
  select(c(Longitude, Latitude, Pred_Yield, Yield_Mg.ha))

colnames(sel_dat) <- c("Longitude", "Latitude", "Predicted_yield", "Actual_yield")

field_save_name <- paste0(selfield, "_Week", best_week, ".csv")

# write.csv(sel_dat, field_save_name, row.names = FALSE)

```




