---
title: "Exponential models with Quantix imagery"
author: "S. Sunoj"
date: "3/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r, message=FALSE, warning=FALSE}
# rm(list = ls())
library(tictoc)  # to monitor time

library(raster) # read raster files
library(rgdal) # Use GDAL functions
library(exactextractr) # Zonal statistics from raster
library(sf) # Working with shapefile layers

library(tidyverse) # data wrangling overall
library(plyr) # data wrangling
library(dplyr) # data wrangling

library(ggpmisc) # To place geom_text within plot
library(plotly) # Interactive visualization
library(patchwork) # This package for arranging multiple ggplots

print("Packages loaded successfully!")

```

# Functions specific to this RMD
```{r}
#########################################
# Creating function for exponential fit
myexpfit <- function(response_var, pred_var, mydata){
  # print(paste0("Model = ", "log(",response_var, ")~", pred_var))
  model.linear <- lm(paste0("log(",response_var, ")~", pred_var), data = mydata)
   a1 <- exp(model.linear$coefficients[1])
   b1 <- (model.linear$coefficients[2])
   R2 <- summary(model.linear)$r.squared

   myresults <- c(a1, b1, R2)
   return(myresults)
}
#########################################

# My GGPLOT for yield map
my_yield_plot <- function(yield_df){
  fieldtitle <- levels(yield_df$Fieldname)
  # Legend labeling - Splitting the yield range into equal classes
  minyld <- round(min(yield_df$Yield_Mg.ha),0) # minimum yield 
  maxyld <- round(max(yield_df$Yield_Mg.ha),0) # maximum yield
  Nclasses <- 4      # Number of yield classes to split from the whole yield range
  
  mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
  YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")

  yld_plot <- ggplot(yield_df, aes(x = Longitude, y = Latitude)) +
  geom_point(aes(color = Yield_Mg.ha), size = 0.7) +    
      theme_bw() +
      # facet_grid(Field~Year, scales = "free") +
      theme(aspect.ratio = 1.0) +
      # ggtitle("Actual yield (Mg/ha)")+
      facet_wrap(~Fieldname, scales = "free") +
      # theme(legend.position = c(0.85, 0.27))+
      scale_colour_gradientn(colours = YE_colors,  
                             name = "Yield (Mg/ha)", 
                             limits=c(minyld,maxyld),
                             breaks = mybreaks,
                             labels = round(mybreaks, 0)) +
    guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
    theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks = element_blank(), 
            plot.title = element_text(size=14, face = "bold")) +
      theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
            legend.text = element_text(vjust = 0.5),
            strip.text = element_text(face = "bold", size = 10))
  yld_plot
  
}

#########################################
my_pred_plot <- function(sub_dat){
  fieldtitle <- levels(sub_dat$Fieldname)
    # Legend labeling - Splitting the yield range into equal classes
  minyld <- round(min(sub_dat$Pred_Yield),0) # minimum yield 
  maxyld <- round(max(sub_dat$Pred_Yield),0) # maximum yield
  Nclasses <- 4      # Number of yield classes to split from the whole yield range
    
  mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
  YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")

  pred_map <- ggplot(sub_dat, aes(x = Longitude, y = Latitude)) +
        geom_point(aes(color = Pred_Yield), size = 0.7) +    
        theme_bw() +
        # facet_grid(Field~Year, scales = "free") +
        theme(aspect.ratio = 1.0) +
        # ggtitle("Predicted yield (Mg/ha)")+
        facet_wrap(~Fieldname, scales = "free") +
        # theme(legend.position = c(0.85, 0.27))+
        scale_colour_gradientn(colours = YE_colors,  
                               name = "Yield (Mg/ha)", 
                               limits=c(minyld,maxyld),
                               breaks = mybreaks,
                               labels = round(mybreaks, 0)) +
        guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(), 
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks = element_blank(), 
              plot.title = element_text(size=14, face = "bold")) +
        theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
              legend.text = element_text(vjust = 0.5),
              strip.text = element_text(face = "bold", size = 10))
  pred_map
}

#########################################
## Actual and predicted yield map
make_yield_maps <- function(sub_datf){

  sel_dat4 <- sub_datf %>% 
    select(Fieldname, Latitude, Longitude, Yield_Mg.ha, Pred_Yield) %>% 
    gather("yield_type", "Value", 4:5) %>% 
    droplevels()
  
  sel_dat4$yield_type <- recode_factor(factor(sel_dat4$yield_type), Pred_Yield = "Predicted yield", Yield_Mg.ha = "Actual yield")
  
  sel_dat4$yield_type <- factor(sel_dat4$yield_type, levels = c("Actual yield", "Predicted yield"))
  
  minyld <- round(min(sel_dat4$Value),0) # minimum yield 
  maxyld <- round(max(sel_dat4$Value),0) # maximum yield
  Nclasses <- 4      # Number of yield classes to split from the whole yield range
    
  mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
  YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")
  
  yld_plot <- ggplot(sel_dat4, aes(x = Longitude, y = Latitude)) +
    geom_point(aes(color = Value), size = 0.7) +    
        theme_bw() +
        # facet_grid(Field~Year, scales = "free") +
        theme(aspect.ratio = 1.0) +
        # ggtitle("Actual yield (Mg/ha)")+
        facet_wrap(~yield_type, scales = "free") +
        # theme(legend.position = c(0.85, 0.27))+
        scale_colour_gradientn(colours = YE_colors,  
                               name = "Yield (Mg/ha)", 
                               limits=c(minyld,maxyld),
                               breaks = mybreaks,
                               labels = round(mybreaks, 0)) +
      guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
      theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(), 
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks = element_blank(), 
              plot.title = element_text(size=14, face = "bold")) +
        theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
              legend.text = element_text(vjust = 0.5),
              strip.text = element_text(face = "bold", size = 10))
  
  yld_plot
}

```

# Load dataset
```{r, message=FALSE, warning=FALSE}

load("Quantix_deep_learning.RData", verbose = TRUE)
str(dat)

r2df_all <- data.frame()

```

# Data preprocessing

## Check for missing values
```{r}
# Check if any columns have missing values 
sapply(dat, anyNA)

# Names of columns that has missing values
names(dat)[sapply(dat, anyNA)]

```


# Plot all yield data
```{r}
g_dat <- dat %>%
  dplyr::filter(Type == "grain") %>%
  droplevels()

my_yield_plot(g_dat)

s_dat <- dat %>%
  dplyr::filter(Type == "silage") %>%
  droplevels()

my_yield_plot(s_dat)

```

# Exploratory data analysis
## Distribution plots
```{r}
# Violin plot

vplt <- ggplot(dat, aes(x = Fieldname, y = Yield_Mg.ha, fill = Fieldname)) +
  geom_violin(alpha = 0.4) +
  theme_bw() +
  facet_wrap(~Type, nrow = 2, scales = "free_y")

vplt


dplt <- ggplot(dat, aes(x = Yield_Mg.ha, y = ..scaled.., fill = Fieldname)) +
  geom_density(alpha = 0.4, size = 1) + 
  theme_bw() +
  facet_wrap(~Type, nrow = 2, scales = "free")

dplt

```

## GPS points vs yield
```{r}

# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
# selfield <- "DMD_GH1"

sub_datf <- dat %>% 
  filter(Week == 1 & Type == "grain") %>% 
  droplevels()

# Legend labeling - Splitting the yield range into equal classes
minyld <- round(min(sub_datf$Yield_Mg.ha),0) # minimum yield 
maxyld <- round(max(sub_datf$Yield_Mg.ha),0) # maximum yield
Nclasses <- 4      # Number of yield classes to split from the whole yield range

mybreaks <- round(seq(minyld, maxyld, len = (Nclasses+1)),0)
YE_colors <-  c("blue","cyan","lightgreen","yellow","orange", "red")

#=====================
lat_plot <- ggplot(sub_datf, aes(x = Latitude, y = Yield_Mg.ha)) +
  geom_point(aes(color = Yield_Mg.ha), size = 0.7) +    
      theme_bw() +
      # facet_grid(Field~Year, scales = "free") +
      theme(aspect.ratio = 1.0) +
      ggtitle("Latitude vs Yield")+
      facet_wrap(~Fieldname, scales = "free") +
      # theme(legend.position = c(0.85, 0.27))+
      scale_colour_gradientn(colours = YE_colors,  
                             name = "Yield (Mg/ha)", 
                             limits=c(minyld,maxyld),
                             breaks = mybreaks,
                             labels = round(mybreaks, 0)) +
    guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
    theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            axis.text.x = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks = element_blank(), 
            plot.title = element_text(size=14, face = "bold")) +
      theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
            legend.text = element_text(vjust = 0.5),
            strip.text = element_text(face = "bold", size = 10))
lat_plot

#=====================
long_plot <- ggplot(sub_datf, aes(x = Longitude, y = Yield_Mg.ha)) +
  geom_point(aes(color = Yield_Mg.ha), size = 0.7) +    
      theme_bw() +
      # facet_grid(Field~Year, scales = "free") +
      theme(aspect.ratio = 1.0) +
      ggtitle("Longitude vs Yield")+
      facet_wrap(~Fieldname, scales = "free") +
      # theme(legend.position = c(0.85, 0.27))+
      scale_colour_gradientn(colours = YE_colors,  
                             name = "Yield (Mg/ha)", 
                             limits=c(minyld,maxyld),
                             breaks = mybreaks,
                             labels = round(mybreaks, 0)) +
    guides(colour = guide_colourbar(barheight = unit(1.8, "in")))+
    theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            axis.text.x = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks = element_blank(), 
            plot.title = element_text(size=14, face = "bold")) +
      theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
            legend.text = element_text(vjust = 0.5),
            strip.text = element_text(face = "bold", size = 10))
long_plot


```

# Approach 1

## 1.a. Use only strip data for exponential model
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
# "1"  "2"  "3"  "4"  "5"  "6"  "7"  "8"  "9"  "10" "11" "12" "13" "14"
# Best grain field - DMD_GH1
# Best silage filed - SSF_121, PSF_12

vi <- c("NDVI", "GNDVI", "EVI2", "SR", "EXG", "TGI")

selfield <- "DMD_GH1"
# seltype <- "silage"

sub_dat <- dat %>% 
  filter(!is.na(N) & Fieldname == selfield) %>% 
  droplevels()

my_yield_plot(sub_dat)

# "1"  "2"  "3"  "4"  "5"  "6"  "7"  "8"  "9"  "10" "11" "12" "13" "14"
lvl <- levels(sub_dat$Week)
sub_dat$Strip <- as.numeric(sub_dat$Strip)

#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(sub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  ggtitle("NDVI vs Yield") +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- sub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()
  
  for (j in 1:length(vi)){
      
    dep_var <- "Yield_Mg.ha"
    ind_var <- vi[j]
    # cat(dep_var, "---", ind_var, "\n")
    
    mod <- myexpfit("Yield_Mg.ha", ind_var, wsub_dat)
    
    ## RMSE calculation ======
    a_fit <- as.numeric(mod[1])
    b_fit <- as.numeric(mod[2])
    rsq <- as.numeric(mod[3])
    
    ssub_dat <- dat %>% 
      filter(Week == lvl[i] & Fieldname == selfield) %>% 
      droplevels() 
      
    ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat[[ind_var]])
  
    ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
    sqe <- (ssub_dat$error^2)
    mse <- mean(sqe)
    rmse_week <- sqrt(mse)
    # cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
    # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
    ## ========================
    
    r2 <- c(as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week)), ind_var)
    r2df <- rbind(r2df, r2)
  }

  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE", "VI")

num_cols <- c("Weeks", "a", "b", "R2", "RMSE")
r2df[num_cols] <- lapply(r2df[num_cols], as.numeric)
str(r2df)

r2df$Fieldname <- rep(selfield, length(lvl))
r2df$Approach <- rep("1a", length(lvl))
r2df_all <- rbind(r2df_all, r2df)

```


```{r, echo = FALSE}
#============================
## Pick the best week
# best_week <- which.max(r2df$R2)
# # best_week <- which.min(r2df$RMSE)
# cat("The best week with max R2 is week ", best_week)
# 
# sub_dat1 <- dat %>% 
#   filter(Week == best_week & Fieldname == selfield) %>% 
#   droplevels()
# 
# a_coeff <- r2df[best_week, 2]
# b_coeff <- r2df[best_week, 3]
# sub_dat1$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat1$NDVI)
# 
# # make_yield_maps(sub_dat1)
# 
# # my_yield_plot(sub_dat1) + my_pred_plot(sub_dat1)
# 
# sub_dat1$error <- (sub_dat1$Pred_Yield - sub_dat1$Yield_Mg.ha)
# mse <- mean(sub_dat1$error^2)
# rmse <- sqrt(mse)
# cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")
# 
# #======================
# # Secondary axis plot
# d  <- r2df
# x  <- 'Weeks'
# y1 <- 'R2'
# y2 <- 'RMSE'
# 
# a            <- range(d[[y1]])
# b            <- range(d[[y2]])
# scale_factor <- diff(a)/diff(b)
# d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]
# 
# trans <- ~ ((. - a[1]) / scale_factor) + b[1]
# 
# r2_rmse_plt <- ggplot(d) +
#               geom_point(aes_string(x, y1)) + 
#               geom_line(aes_string(x, y1)) + 
#               geom_point(aes_string(x, y2), col='red') + 
#               geom_line(aes_string(x, y2), col='red') +
#               ggtitle(selfield) + 
#               theme_bw()+
#               theme(legend.position = c(0.8, 0.7)) + 
#               scale_x_continuous(breaks = seq(1,15, 1))+
#               scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))
# 
# r2_rmse_plt

# 
# ggplotly(r2_rmse_plt)
```

## 1.b. Use lower and upper 10% of strip data
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
selfield <- "SSF_66"

sub_dat <- dat %>% 
  filter(!is.na(N) & Fieldname == selfield) %>%
  droplevels()
my_yield_plot(sub_dat)

# Evaluate qunatile cutoffs
pert <- 0.10

cutoffs <- quantile(sub_dat$Yield_Mg.ha, c(pert, (1-pert)))
cat("Cutoff for field", selfield, " =", cutoffs)

# Subset points within cutoff
qsub_dat <- sub_dat %>% 
  filter(Yield_Mg.ha <= cutoffs[[1]] | Yield_Mg.ha >= cutoffs[[2]]) %>% 
  droplevels()

my_yield_plot(qsub_dat)

#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(qsub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

lvl <- levels(qsub_dat$Week)

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- qsub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()

    for (j in 1:length(vi)){
      
      dep_var <- "Yield_Mg.ha"
      ind_var <- vi[j]
      # cat(dep_var, "---", ind_var, "\n")
      
      mod <- myexpfit("Yield_Mg.ha", ind_var, wsub_dat)
     
      ## RMSE calculation ======
      a_fit <- as.numeric(mod[1])
      b_fit <- as.numeric(mod[2])
      rsq <- as.numeric(mod[3])
      
      ssub_dat <- dat %>% 
        filter(Week == lvl[i] & Fieldname == selfield) %>% 
        droplevels() 
        
      ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat[[ind_var]])
    
      ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
      sqe <- (ssub_dat$error^2)
      mse <- mean(sqe)
      rmse_week <- sqrt(mse)
      # cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
      # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
      ## ========================
      
      r2 <- c(as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week)), ind_var)
      r2df <- rbind(r2df, r2)
    }
  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE", "VI")

num_cols <- c("Weeks", "a", "b", "R2", "RMSE")
r2df[num_cols] <- lapply(r2df[num_cols], as.numeric)
str(r2df)

r2df$Fieldname <- rep(selfield, length(lvl))
r2df$Approach <- rep("1b", length(lvl))
r2df_all <- rbind(r2df_all, r2df)
```


```{r, echo = FALSE}
#==========================================
## Select best week and evaluate RMSE
# best_week <- which.max(r2df$R2)
# cat("The best week with max R2 is week ", best_week)
# 
# sub_dat2 <- dat %>% 
#   filter(Week == best_week & Fieldname == selfield)
# 
# a_coeff <- r2df[best_week, 2]
# b_coeff <- r2df[best_week, 3]
# sub_dat2$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat2[["NDVI"]])
# 
# make_yield_maps(sub_dat2)
# # my_yield_plot(sub_dat2) + my_pred_plot(sub_dat2)
# 
# sub_dat2$error <- (sub_dat2$Pred_Yield - sub_dat2$Yield_Mg.ha)
# se <- (sub_dat2$error^2)
# mse <- mean(se)
# rmse <- sqrt(mse)
# cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")
# 
# #======================
# # Secondary axis plot
# d  <- r2df
# x  <- 'Weeks'
# y1 <- 'R2'
# y2 <- 'RMSE'
# 
# a            <- range(d[[y1]])
# b            <- range(d[[y2]])
# scale_factor <- diff(a)/diff(b)
# d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]
# 
# trans <- ~ ((. - a[1]) / scale_factor) + b[1]
# 
# r2_rmse_plt <- ggplot(d) +
#               geom_point(aes_string(x, y1)) + 
#               geom_line(aes_string(x, y1)) + 
#               geom_point(aes_string(x, y2), col='red') + 
#               geom_line(aes_string(x, y2), col='red') +
#               ggtitle(selfield) + 
#               theme_bw()+
#               theme(legend.position = c(0.8, 0.7)) + 
#               scale_x_continuous(breaks = seq(1,15, 1))+
#               scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))
# 
# r2_rmse_plt
# ggplotly(r2_rmse_plt)

```

# Approach 2

## 2.a. Use whole field data without strip --> is.na(N)
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
selfield <- "SSF_66"

sub_dat <- dat %>% 
  filter(is.na(N) & Fieldname == selfield) %>% 
  droplevels()

my_yield_plot(sub_dat)

#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(sub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

lvl <- levels(sub_dat$Week)

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- sub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()
  
    for (j in 1:length(vi)){
      
      dep_var <- "Yield_Mg.ha"
      ind_var <- vi[j]
      # cat(dep_var, "---", ind_var, "\n")
      
      mod <- myexpfit("Yield_Mg.ha", ind_var, wsub_dat)
    
      ## RMSE calculation ======
      a_fit <- as.numeric(mod[1])
      b_fit <- as.numeric(mod[2])
      rsq <- as.numeric(mod[3])
      
      ssub_dat <- dat %>% 
        filter(Week == lvl[i] & Fieldname == selfield) %>% 
        droplevels() 
        
      ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat[[ind_var]])
    
      ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
      sqe <- (ssub_dat$error^2)
      mse <- mean(sqe)
      rmse_week <- sqrt(mse)
      # cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
      # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
      ## ========================
      
      r2 <- c(as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week)), ind_var)
      r2df <- rbind(r2df, r2)
  }
  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE", "VI")

num_cols <- c("Weeks", "a", "b", "R2", "RMSE")
r2df[num_cols] <- lapply(r2df[num_cols], as.numeric)
str(r2df)

r2df$Fieldname <- rep(selfield, length(lvl))
r2df$Approach <- rep("2a", length(lvl))
r2df_all <- rbind(r2df_all, r2df)

```


```{r, echo = FALSE}
#==========================================
## Select best week and evaluate RMSE
# best_week <- which.max(r2df$R2)
# cat("The best week with max R2 is week ", best_week)
# 
# sub_dat3 <- dat %>% 
#   filter(Week == best_week & Fieldname == selfield)
# 
# a_coeff <- r2df[best_week, 2]
# b_coeff <- r2df[best_week, 3]
# sub_dat3$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat3$NDVI)
# 
# make_yield_maps(sub_dat3)
# # my_yield_plot(sub_dat3) + my_pred_plot(sub_dat3)
# 
# sub_dat3$error <- (sub_dat3$Pred_Yield - sub_dat3$Yield_Mg.ha)
# mse <- mean(sub_dat3$error^2)
# rmse <- sqrt(mse)
# cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")
# 
# #======================
# # Secondary axis plot
# d  <- r2df
# x  <- 'Weeks'
# y1 <- 'R2'
# y2 <- 'RMSE'
# 
# a            <- range(d[[y1]])
# b            <- range(d[[y2]])
# scale_factor <- diff(a)/diff(b)
# d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]
# 
# trans <- ~ ((. - a[1]) / scale_factor) + b[1]
# 
# r2_rmse_plt <- ggplot(d) +
#               geom_point(aes_string(x, y1)) + 
#               geom_line(aes_string(x, y1)) + 
#               geom_point(aes_string(x, y2), col='red') + 
#               geom_line(aes_string(x, y2), col='red') +
#               ggtitle(selfield) + 
#               theme_bw()+
#               theme(legend.position = c(0.8, 0.7)) + 
#               scale_x_continuous(breaks = seq(1,15, 1))+
#               scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))
# 
# r2_rmse_plt
# ggplotly(r2_rmse_plt)

```

## 2.b. Use lower and upper 10% of whole field data
```{r}
# "DMD_GH1" "PSF_111" "PSF_12"  "SLS_ABH" "SLS_NS"  "SSF_121" "SSF_202" "SSF_66"
selfield <- "SSF_66"

sub_dat <- dat %>% 
  filter(is.na(N) & Fieldname == selfield) %>% 
  droplevels()

my_yield_plot(sub_dat)

# Evaluate quantile cutoffs
pert <- 0.10
cutoffs <- quantile(sub_dat$Yield_Mg.ha, c(pert, (1-pert)))
cat("Cutoff for field", selfield, " =", cutoffs)

# Subset points within cutoff
qsub_dat <- sub_dat %>% 
  filter(Yield_Mg.ha <= cutoffs[[1]] | Yield_Mg.ha >= cutoffs[[2]]) %>% 
  droplevels()

my_yield_plot(qsub_dat)

#==============
# Scatter plot between NDVI and Yield
sct_plt <- ggplot(qsub_dat, aes(x = NDVI, y = Yield_Mg.ha)) + 
  geom_point(aes(color = Week)) +
  theme_bw() + 
  theme(aspect.ratio = 1) +
  xlab("NDVI") + 
  ylab("Yield (Mg/ha)") + 
  xlim(c(0.0, 1.0))

sct_plt
#==============

lvl <- levels(qsub_dat$Week)

r2df <- data.frame()
for (i in 1:length(lvl)){
  # print(i)
  wsub_dat <- qsub_dat %>% 
    filter(Week == lvl[i]) %>%
    droplevels()
  
    for (j in 1:length(vi)){
      
      dep_var <- "Yield_Mg.ha"
      ind_var <- vi[j]
      # cat(dep_var, "---", ind_var, "\n")
      
      mod <- myexpfit("Yield_Mg.ha", ind_var, wsub_dat)
      
      ## RMSE calculation ======
      a_fit <- as.numeric(mod[1])
      b_fit <- as.numeric(mod[2])
      rsq <- as.numeric(mod[3])
      
      ssub_dat <- dat %>% 
        filter(Week == lvl[i] & Fieldname == selfield) %>% 
        droplevels() 
        
      ssub_dat$Pred_Yield <-  a_fit*exp(b_fit*ssub_dat[[ind_var]])
    
      ssub_dat$error <- (ssub_dat$Pred_Yield - ssub_dat$Yield_Mg.ha)
      sqe <- (ssub_dat$error^2)
      mse <- mean(sqe)
      rmse_week <- sqrt(mse)
      cat(lvl[i], ") a_fit = ", a_fit, "; b_fit = ", b_fit, ";\t R2 = ", rsq,";\t RMSE = ", rmse_week, "\n")
      # cat("RMSE for", selfield, "on week", lvl[i], "is", rmse, "Mg/ha")
      ## ========================
  
      r2 <- c(as.numeric(c(lvl[i], mod[1], mod[2], mod[3], rmse_week)), ind_var)  
      r2df <- rbind(r2df, r2)
  }
  # print(paste0(i, " = ", mod[3]))
}

colnames(r2df) <- c("Weeks", "a", "b", "R2", "RMSE", "VI")
num_cols <- c("Weeks", "a", "b", "R2", "RMSE")
r2df[num_cols] <- lapply(r2df[num_cols], as.numeric)
str(r2df)

r2df$Fieldname <- rep(selfield, length(lvl))
r2df$Approach <- rep("2b", length(lvl))
r2df_all <- rbind(r2df_all, r2df)
```


```{r, echo = FALSE}
#==========================================
## Select best week and evaluate RMSE
# best_week <- which.max(r2df$R2)
# cat("The best week with max R2 is week ", best_week)
# 
# sub_dat4 <- dat %>% 
#   filter(Week == best_week & Fieldname == selfield) %>% 
#   droplevels()
# 
# a_coeff <- r2df[best_week, 2]
# b_coeff <- r2df[best_week, 3]
# 
# sub_dat4$Pred_Yield <-  a_coeff*exp(b_coeff*sub_dat4$NDVI)
# 
# make_yield_maps(sub_dat4)
# # my_yield_plot(sub_dat4) + my_pred_plot(sub_dat4)
# 
# sub_dat4$error <- (sub_dat4$Pred_Yield - sub_dat4$Yield_Mg.ha)
# mse <- mean(sub_dat4$error^2)
# rmse <- sqrt(mse)
# cat("RMSE for", selfield, "on week", best_week, "is", rmse, "Mg/ha")
# 
# #======================
# # Secondary axis plot
# d  <- r2df
# x  <- 'Weeks'
# y1 <- 'R2'
# y2 <- 'RMSE'
# 
# #-----------------------------------------------------------------------------
# # Rescale the second y axis by 
# #   - subtracting its minimum value (to set it to start at 0)
# #   - scaling so that it has the same range as the 'y1' variable
# #   - offsettting it by the minimum value of y1
# #-----------------------------------------------------------------------------
# a            <- range(d[[y1]])
# b            <- range(d[[y2]])
# scale_factor <- diff(a)/diff(b)
# d[[y2]]      <- ((d[[y2]] - b[1]) * scale_factor) + a[1]
# 
# #-----------------------------------------------------------------------------
# # Need to define the second axis transformation to be the inverse of the data
# # transformation to everything cancels out appropriately
# #-----------------------------------------------------------------------------
# trans <- ~ ((. - a[1]) / scale_factor) + b[1]
# 
# #-----------------------------------------------------------------------------
# # tell the y axis to set up a scaled secondary axis with the given transform
# #-----------------------------------------------------------------------------
# r2_rmse_plt <- ggplot(d) +
#               geom_point(aes_string(x, y1)) + 
#               geom_line(aes_string(x, y1)) + 
#               geom_point(aes_string(x, y2), col='red') + 
#               geom_line(aes_string(x, y2), col='red') +
#               ggtitle(selfield) + 
#               theme_bw()+
#               theme(legend.position = c(0.8, 0.7)) + 
#               scale_x_continuous(breaks = seq(1,15, 1))+
#               scale_y_continuous(sec.axis = sec_axis(trans=trans, name=y2))
# 
# r2_rmse_plt

# ggplotly(r2_rmse_plt)
```


# All vegetation indices + All weeks + All fields
```{r}

load("Exponential_results_March31.RData", verbose = TRUE)

```



# Plotting performance data - All VI + All weeks + All fields + All approaches
```{r, fig.width=12, fig.height=8}
# "DMD_GH1", "SLS_ABH", "SLS_NS", "SSF_121" "SSF_66", "SSF_202", "PSF_111", "PSF_12"  
# selfield <- "DMD_GH1"

# results_df$yield_type <- recode_factor(factor(sel_dat4$yield_type), Pred_Yield = "Predicted yield", Yield_Mg.ha = "Actual yield")
  
results_df$VI <- factor(results_df$VI, levels = c("TGI", "EXG", "SR", "GNDVI", "EVI2", "NDVI"))

# selVI <- "EVI2"

sub_results <- results_df %>% 
  # filter(Fieldname == selfield) %>% 
  droplevels()

bar_plot<-ggplot(data=sub_results, aes(x=Weeks, y=R2, fill=VI)) +
  # geom_bar(stat="identity", position=position_dodge(0.8), width = 0.7) +
  geom_bar(stat="identity", position=position_dodge(), width = 0.6) +
  theme_bw() +
  theme(legend.position = "right", legend.box = "horizontal") +
  # theme(legend.position = "none") +
  # guides(colour = guide_legend(nrow = 1)) + 
  # ggtitle(selfield) + 
  # facet_wrap(~Approach) +
  facet_grid(Fieldname~Approach) + 
  # facet_grid(Fieldname~Approach) + 
  scale_x_continuous(breaks = seq(1, 14, 1)) +
  # scale_y_continuous(expand = c(0, 0)) + 
  scale_y_continuous(expand = c(0, 0), breaks = seq(0.0, 1.05, 0.2), limits = c(0.0, 1.05)) +
  # geom_text(aes(label=round(R2,2)), vjust=0.5, hjust = -0.2,  color="black",
  #           position = position_dodge(0), size=2, angle = 90)+
  # scale_fill_brewer(palette="Reds") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.title = element_text(size = 10, face = "bold"),
        # axis.title.y = element_blank(),
        axis.text = element_text(size = 8, color = "black"),
        # axis.text.y = element_blank(),
        # axis.ticks.length=unit(-1.5, "mm"),
        plot.title = element_text(size=14, face = "bold")) +
  theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
        legend.text = element_text(vjust = 0.5),
        strip.text = element_text(face = "bold", size = 10)) 
  
bar_plot

# ggplotly(bar_plot)

# ggsave("All_VI_performance.pdf", width = 12, height = 8, units = "in")

```



# Plotting performance data - NDVI
```{r, fig.width=12, fig.height=8}
# "DMD_GH1", "SLS_ABH", "SLS_NS", "SSF_121" "SSF_66", "SSF_202", "PSF_111", "PSF_12"  
# selfield <- "SSF_66"

# results_df$yield_type <- recode_factor(factor(sel_dat4$yield_type), Pred_Yield = "Predicted yield", Yield_Mg.ha = "Actual yield")
  
results_df$Fieldname <- factor(results_df$Fieldname, levels = c("DMD_GH1", "SLS_ABH", "SLS_NS", "SSF_121", "SSF_66", "SSF_202", "PSF_111", "PSF_12"))

selVI <- "NDVI"

sub_results <- results_df %>% 
  filter(VI == selVI) %>% 
  droplevels()

bar_plot<-ggplot(data=sub_results, aes(x=Weeks, y=R2, fill=VI)) +
  geom_bar(stat="identity", position=position_dodge(0.8), width = 0.7, fill = "lightseagreen") +
  theme_bw() +
  # theme(legend.position = "bottom", legend.box = "horizontal") + 
  theme(legend.position = "none") +
  guides(colour = guide_legend(nrow = 1)) + 
  ggtitle(selVI) + 
  facet_grid(Fieldname~Approach) + 
  scale_x_continuous(breaks = seq(1, 14, 1)) +
  scale_y_continuous(expand = c(0, 0), breaks = seq(0.0, 1.05, 0.2), limits = c(0.0, 1.05)) +
  geom_text(aes(label=round(R2,2)), vjust=0.5, hjust = -0.2,  color="black",
            position = position_dodge(0), size=2, angle = 90)+
  # scale_fill_brewer(palette="Reds") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.title = element_text(size = 10, face = "bold"),
        # axis.title.y = element_blank(),
        axis.text = element_text(size = 8, color = "black"),
        # axis.text.y = element_blank(),
        # axis.ticks.length=unit(-1.5, "mm"),
        plot.title = element_text(size=14, face = "bold")) +
  theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
        legend.text = element_text(vjust = 0.5),
        strip.text = element_text(face = "bold", size = 10)) 
  
bar_plot

# ggsave("VI_performance.pdf", width = 8.5, height = 11, units = "in")

```




# Plotting performance data - EVI2
```{r, fig.width=12, fig.height=8}
# "DMD_GH1", "SLS_ABH", "SLS_NS", "SSF_121" "SSF_66", "SSF_202", "PSF_111", "PSF_12"  
# selfield <- "SSF_66"

# results_df$yield_type <- recode_factor(factor(sel_dat4$yield_type), Pred_Yield = "Predicted yield", Yield_Mg.ha = "Actual yield")
  
results_df$Fieldname <- factor(results_df$Fieldname, levels = c("DMD_GH1", "SLS_ABH", "SLS_NS", "SSF_121", "SSF_66", "SSF_202", "PSF_111", "PSF_12"))

selVI <- "EVI2"

sub_results <- results_df %>% 
  filter(VI == selVI) %>% 
  droplevels()

bar_plot<-ggplot(data=sub_results, aes(x=Weeks, y=R2, fill=VI)) +
  geom_bar(stat="identity", position=position_dodge(0.8), width = 0.7, fill = "lightseagreen") +
  theme_bw() +
  # theme(legend.position = "bottom", legend.box = "horizontal") + 
  theme(legend.position = "none") +
  guides(colour = guide_legend(nrow = 1)) + 
  ggtitle(selVI) + 
  facet_grid(Fieldname~Approach) + 
  scale_x_continuous(breaks = seq(1, 14, 1)) +
  scale_y_continuous(expand = c(0, 0), breaks = seq(0.0, 1.05, 0.2), limits = c(0.0, 1.05)) +
  geom_text(aes(label=round(R2,2)), vjust=0.5, hjust = -0.2,  color="black",
            position = position_dodge(0), size=2, angle = 90)+
  # scale_fill_brewer(palette="Reds") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.title = element_text(size = 10, face = "bold"),
        # axis.title.y = element_blank(),
        axis.text = element_text(size = 8, color = "black"),
        # axis.text.y = element_blank(),
        # axis.ticks.length=unit(-1.5, "mm"),
        plot.title = element_text(size=14, face = "bold")) +
  theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
        legend.text = element_text(vjust = 0.5),
        strip.text = element_text(face = "bold", size = 10)) 
  
bar_plot

# ggsave("VI_performance.pdf", width = 8.5, height = 11, units = "in")

```



# Plotting performance data - GNDVI
```{r, fig.width=12, fig.height=8}
# "DMD_GH1", "SLS_ABH", "SLS_NS", "SSF_121" "SSF_66", "SSF_202", "PSF_111", "PSF_12"  
# selfield <- "SSF_66"

# results_df$yield_type <- recode_factor(factor(sel_dat4$yield_type), Pred_Yield = "Predicted yield", Yield_Mg.ha = "Actual yield")
  
results_df$Fieldname <- factor(results_df$Fieldname, levels = c("DMD_GH1", "SLS_ABH", "SLS_NS", "SSF_121", "SSF_66", "SSF_202", "PSF_111", "PSF_12"))

selVI <- "GNDVI"

sub_results <- results_df %>% 
  filter(VI == selVI) %>% 
  droplevels()

bar_plot<-ggplot(data=sub_results, aes(x=Weeks, y=R2, fill=VI)) +
  geom_bar(stat="identity", position=position_dodge(0.8), width = 0.7, fill = "lightseagreen") +
  theme_bw() +
  # theme(legend.position = "bottom", legend.box = "horizontal") + 
  theme(legend.position = "none") +
  guides(colour = guide_legend(nrow = 1)) + 
  ggtitle(selVI) + 
  facet_grid(Fieldname~Approach) + 
  scale_x_continuous(breaks = seq(1, 14, 1)) +
  scale_y_continuous(expand = c(0, 0), breaks = seq(0.0, 1.05, 0.2), limits = c(0.0, 1.05)) +
  geom_text(aes(label=round(R2,2)), vjust=0.5, hjust = -0.2,  color="black",
            position = position_dodge(0), size=2, angle = 90)+
  # scale_fill_brewer(palette="Reds") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.title = element_text(size = 10, face = "bold"),
        # axis.title.y = element_blank(),
        axis.text = element_text(size = 8, color = "black"),
        # axis.text.y = element_blank(),
        # axis.ticks.length=unit(-1.5, "mm"),
        plot.title = element_text(size=14, face = "bold")) +
  theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
        legend.text = element_text(vjust = 0.5),
        strip.text = element_text(face = "bold", size = 10)) 
  
bar_plot

# ggsave("VI_performance.pdf", width = 8.5, height = 11, units = "in")

```


# Week 6 and 7 - Three VI + All approaches + All fields

```{r, fig.width = 12, fig.height = 8}

sel_dat <- results_df %>% 
  filter(Weeks == 6 | Weeks == 7) %>% 
  filter(VI == "NDVI" | VI == "GNDVI" | VI == "EVI2") %>% 
  droplevels()

bar_plot<-ggplot(data=sel_dat, aes(x=Weeks, y=R2, fill=VI)) +
  geom_bar(stat="identity", position=position_dodge(0.8), width = 0.7) +
  theme_bw() +
  # theme(legend.position = "bottom", legend.box = "horizontal") + 
  theme(legend.position = "right") +
  guides(colour = guide_legend(nrow = 1)) + 
  # ggtitle(selVI) + 
  facet_grid(Fieldname~Approach) + 
  scale_x_continuous(breaks = seq(1, 14, 1)) +
  scale_y_continuous(expand = c(0, 0), breaks = seq(0.0, 1.05, 0.2), limits = c(0.0, 1.05)) +
  # geom_text(aes(label=round(R2,2)), vjust=0.5, hjust = -0.2,  color="black",
  #           position = position_dodge(0), size=2, angle = 90)+
  # scale_fill_brewer(palette="Reds") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.title = element_text(size = 10, face = "bold"),
        # axis.title.y = element_blank(),
        axis.text = element_text(size = 8, color = "black"),
        # axis.text.y = element_blank(),
        # axis.ticks.length=unit(-1.5, "mm"),
        plot.title = element_text(size=14, face = "bold")) +
  theme(legend.title = element_text(face = "bold", size=8, margin = margin(0,0,7,0)),
        legend.text = element_text(vjust = 0.5),
        strip.text = element_text(face = "bold", size = 10)) 
  
bar_plot

```



